A data-driven, pixel-level model to improve the precision of \Kepler\ photometry

### 2013-10-26 documents/plm.tex
PLM pixels, PLM photometry, interpretation

In some sense, it is this residual that contains the exoplanet transit signals we seek.
That is, a transit creates a negative residual away from the prediction.
So far, however, the model is a model of \emph{pixels},
  and we need to obtain from this model \emph{photometric measurements} of stars.
In order to construct stellar photometry measurements out of the residual pixels $\delta_{mn}$,
  we add into each pixel residual $\delta_{mn}$ the \emph{mean predicted intensity} $\bar{I}^{\ast}_m$
\begin{eqnarray}
\bar{I}^{\ast}_m &=& \frac{1}{N_m}\,\sum_n I^{\ast}_{mnn}
\quad ,
\end{eqnarray}
where $N_m$ is the number of time steps in the quarter,
  and the sum is over those time steps.
We construct what we will call ``the \name\ photometry''
  from what we will call ``the \name\ pixels'' $J_{mn}$,
  which are the residuals plus the mean, or
\begin{eqnarray}
J_mn &=& \delta_{mn} + \bar{I}^{\ast}_m
\quad .
\end{eqnarray}
That is, \todo{WTF}

\todo{HOGG: We construct the \name\ photometry from the \name\ pixels how?}

\todo{Hogg \& DFM:  Why does the above make no fucking sense?}

>>>>

In some sense, it is this residual that contains the exoplanet transit signals we seek.
That is, a transit creates a negative residual away from the prediction.
So far, however, the model is a model of \emph{pixels},
  and we need to obtain from this model \emph{photometric measurements} of stars.
In order to construct stellar photometry measurements out of the residual pixels $\delta_{mn}$,
  we add into each pixel residual $\delta_{mn}$ the \emph{mean predicted intensity} $\bar{I}^{\ast}_m$
\begin{eqnarray}
\bar{I}^{\ast}_m &=& \frac{1}{N_m}\,\sum_n I^{\ast}_{mnn}
\quad ,
\end{eqnarray}
where $N_m$ is the number of time steps in the quarter,
  and the sum is over those time steps.
We construct what we will call ``the \name\ pixels'' $J_{mn}$,
  which are the residuals plus the mean, or
\begin{eqnarray}
J_{mn} &=& \delta_{mn} + \bar{I}^{\ast}_m
\quad .
\end{eqnarray}
\todo{DFM: Should we use mean or median here?}
That is, we treat each pixel as differing from constant intensity
  only inasmuch as it has residuals away from the model prediction.

Our new stellar flux estimates,
  what we will call the ``\name\ photometry'',
  is constructed from the \name\ pixels
  in precisely the same way as the official \Kepler\ SAP photometry
  is constructed from the Target Pixel Files.
That is, we perform a weighted sum of \name\ pixels $J_{mn}$ with weights $w_m$,
  all of which are either zero or unity,
  and we adopt precisely the same weight assignments as are adopted in the SAP photometry;
  in equations, the flux estimate $S_n$ at time $t_n$ of the target star is given by
\begin{eqnarray}
S_n = \frac{1}{N_m}\,\sum_n w_m\,J_{mn}
\quad .
\end{eqnarray}
As we have noted above and below, these photometric estimators are not optimal for any purpose,
  but improving them is beyond the scope of this project.

Some---or probably most---of the variations of the pixel intensities
  are being caused by small changes to stellar positions relative to the detector,
  in turn caused by pointing drifts, parallaxes, proper motions, aberration, and temperature changes.
The \name\ pixels, being constructed from a mean prediction plus residuals,
  represent some kind of mean image, averaged over these positional changes.
  that is, the image constructed from the \name\ pixels would have a broader
  point-spread function than any individual time-step,
  and does not necessarily represent any true astronomical scene.
This is another consequence of the point, discussed above,
  that data-driven models do not in general provide interpretable results.
This uninterpretability creates a small problem,
  which is that the optimization by which the \Kepler\ team chose the pixel weights $w_m$
  cannot be precisely appropriate for the \name\ pixels,
  even if it \emph{is} appropriate for the \Kepler\ Target Pixel Files.
That is, there could be a small sacrifice at this step in photometric estimator quality.
This motivates future work on photometric estimation.
That said, we don't expect this effect to be large,
  because the positional drifts involved are orders of magnitude smaller than a pixel.
